### 2019-12-18 Draft_V5.tex
up

\newpage
\tableofcontents
\newpage
\section{Model, asymptotic property of LS and IV estimator}
\subsection{The models and Assumptions}
\subsubsection{Fixed effects model}
Consider the dynamic heterogeneous panels data model with fixed effects:
\begin{align}
\begin{split}
y_{i,t}&=\alpha_{i}+\phi_{i} y_{i,t-1}+ \boldsymbol{x}^{'}_{i,t}\boldsymbol{\beta}_{i}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T\, , \\
&= \boldsymbol{w}^{'}_{i,t}\boldsymbol{\theta}+ \alpha_{i}+u_{i,t}, \label{1}
\end{split}
\end{align}
where $\boldsymbol{x}_{i,t}$ and $\boldsymbol{\beta}_{i}$ are $k \times 1$ vectors and $\boldsymbol{w}_{i,t}=\left(\phi_{i}, \boldsymbol{\beta}^{'}_{i} \right)^{'}$ is a $\left(1+k\right) \times 1$ vector.
Stacking the $T$ observations for each $i$, we have
\begin{align}
\boldsymbol{y}_{i}=\boldsymbol{W}_{i}\boldsymbol{\theta}_{i}+ \alpha_{i}\boldsymbol{\iota}_{T}+ \boldsymbol{u}_{i}, \label{2}
\end{align}
where $\boldsymbol{y}_{i}=\left(y_{i,1},\ldots, y_{i,T} \right)^{'}$, $\boldsymbol{W}_{i}=\left(\boldsymbol{w}_{i,1},\ldots, \boldsymbol{w}_{i,T} \right)^{'}$, $\iota_{T}=\left(1,\ldots,1 \right)^{'}$ and $\boldsymbol{u}_{i}=\left(u_{i,1}, \ldots, u_{i,T} \right)^{'}$.

@@

\subsection{IV estimator}
We use current and lagged values of $\boldsymbol{x}_{i}$ as instruments, as
\begin{align}
\boldsymbol{Z}^{(j)}_{i}=\left( \boldsymbol{x}_{i,\cdot}, \boldsymbol{x}_{i,-1},\ldots, \boldsymbol{x}_{i,-j} \right)^{'},
\end{align}
where $\boldsymbol{Z}^{(j)}_{i}$ is $T \times  (j+1)k$ matrix with $j \geq 1$. \\

@@

\citet{Kuersteiner:2010} provided model averaging two stage least squares estimator to balance the bias and efficiency. We try to follow this method to construct the optimal instruments. We define a weighting vector $\boldsymbol{W}=\left(w_{1}, \ldots, w_{j} \right)^{'}$. Then, we can weight $\boldsymbol{P}^{(j)}_{i}$ as
\begin{align}
\boldsymbol{P}\left(\boldsymbol{W} \right)= \sum^{J}_{j=1}w_{j} \boldsymbol{P}^{(j)}_{i},
\end{align}
where $J$ is maximum number of lagged variables that we can observed. 
Our goal is choosing $\boldsymbol{W}$ to minimize the approximate mean square error.

\subsection{Asymptotic property of LS estimator}

@@

\subsection{Asymptotic property of IV estimator}
We use current and lagged values of $\boldsymbol{x}_{i}$ as instruments, as
\begin{align}
\tilde{\boldsymbol{Z}}_{i,t}=\left( \tilde{\boldsymbol{x}}_{i}, \tilde{\boldsymbol{x}}_{i,-1} \right)^{'},
\end{align}
where $\tilde{\boldsymbol{Z}}_{i}$ is $T \times  2$ vector. \\

\begin{myAssu}
$\boldsymbol{A}_{i}=\plim_{T \to \infty}\tilde{\boldsymbol{A}}_{i,T}$ has full column rank, $\boldsymbol{B}_{i}=\plim_{T \to \infty}\tilde{\boldsymbol{B}}_{i,T}$ and $\boldsymbol{\Sigma}_{i}=\plim_{T \to \infty} T^{-1}\boldsymbol{Z}^{'}_{i}\boldsymbol{u}_{i} \boldsymbol{u}_{i}^{'}\boldsymbol{Z}$ has positive definite, uniformly, where $\tilde{\boldsymbol{A}}_{i,T}= \frac{1}{T}\tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{W}}_{i}$ and $\tilde{\boldsymbol{B}}_{i,T}= \frac{1}{T}\tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{Z}}_{i}$ \\
\end{myAssu}

Then, the IV estimator can be expressed as
\begin{align}
\boldsymbol{\hat{\theta}}_{IV,i}=\left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{g}}_{i,T},
\end{align}
where
\begin{align}
\tilde{\boldsymbol{g}}_{i,T}=\frac{1}{T}\tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{y}}_{i},
\end{align}
 and $\tilde{\boldsymbol{W}}_{i}=\left( \tilde{w}^{'}_{i,1},\ldots, \tilde{w}^{'}_{i,T} \right)^{'}$ is $T \times 2$ matrix

From above equation, we have
\begin{align}
\sqrt{T}\left(\boldsymbol{\hat{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)=\left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\left(T^{-1/2}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \right)
\end{align}
Then, the property of $T^{-1/2}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} $ is given by following proposition.\\
\begin{myProp}
Under above assumptions, as $\left(N, T \right)\overset{j}{\to} \infty$ such that $N/T \to c$ with $0 < c<\infty $, for each $i$, we have
\begin{align}
\begin{split}
&N^{-1} \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i}\overset{p}{\to} \boldsymbol{0},  \\
&\,\,\,\,and\,\,\,\,\, \\
&T^{-1/2}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{i} \right).
\end{split}
\end{align}
\end{myProp}

Thus, IV  estimator, $\boldsymbol{\theta}_{IV, i}$ is $\sqrt{T}$ consistent to $\boldsymbol{\theta}_{i}$ and this estimator does not have Nickell's bias. Then, we have following theorem\\
$\mathbf{Theorem \,\,1}$ \\
As $\left(N,T \right)\to \infty $ such that $N/T \to c$ with $0< c< \infty$. for each $i$,
\begin{align}
\sqrt{T}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right)\overset{d}{\to} N \left(\boldsymbol{0},\,\left(\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}\boldsymbol{A}_{i} \right)^{-1}\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}   \boldsymbol{\Sigma}_{i}\boldsymbol{B}_{i}^{-1} \boldsymbol{A}_{i}\left(\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}\boldsymbol{A}_{i} \right)\right).
\end{align}

\subsubsection{Mean group IV estimator }
Now, we define the mean group estimator of $\boldsymbol{\theta}$:
\begin{align}
\hat{\boldsymbol{\theta}}_{IVMG}=\frac{1}{N}\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}_{IVi}.
\end{align}
And we can show that the asymptotic property of $\hat{\boldsymbol{\theta}}_{IVMG}$, as
\begin{align}
\hat{\boldsymbol{\theta}}_{IVMG}-\boldsymbol{\theta}=\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}\right)=\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}_{i}\right)+\frac{1}{N}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i},
\end{align}
where
\begin{align}
\begin{split}
\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}_{i}\right)&=\frac{1}{N}\sum^{N}_{i=1} \left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)^{-1}\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\left(T^{-1}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \right) \\
&= O_{p}\left(\delta^{-2}_{NT} \right),
\end{split}
\end{align}
where $\delta_{NT}=\min \{\sqrt{N},\,\sqrt{T} \}$.
We note that $\frac{1}{\sqrt{N}}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i}=O_{p}\left(N^{-1/2} \right)$, if $\delta_{NT}^{-(2+\varsigma)}\to 0$ for any $\varsigma >0$, we have
\begin{align}
\sqrt{N}\left(\hat{\boldsymbol{\theta}}_{IVMG}-\boldsymbol{\theta}  \right)=\frac{1}{\sqrt{N}}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i}+o_{p} \left(1 \right).
\end{align}

And the variance estimator of $\hat{\boldsymbol{\theta}}_{IVMG}$ is given by
\begin{align}
\hat{\boldsymbol{\Sigma}}_{IV,\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{IV,i}- \hat{\boldsymbol{\theta}}_{IVMG}\right)\left( \hat{\boldsymbol{\theta}}_{IV,i}- \hat{\boldsymbol{\theta}}_{IVMG}\right)^{'}. \label{44}
\end{align}
Follow \citet{Norkute:2019}, we can show that $\hat{\boldsymbol{\Sigma}}_{IV,\lambda}$ is consistent and it does not have small $T$ bias.
Firstly, we decompose $(\ref{44})$ as
\begin{align}
\begin{split}
&\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}_{IVMG}\right)\left( \hat{\boldsymbol{\theta}}_{IV,i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}_{IVMG}\right)^{'}= \\
& \sum^{N}_{i=1} \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)^{'}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) -\\
&N\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right). \label{45}
\end{split}
\end{align}
Then we can show consistent of $\hat{\boldsymbol{\Sigma}}_{IV,\lambda}$ as
\begin{align}
\begin{split}
&\hat{\boldsymbol{\Sigma}}_{IV,\lambda}-\boldsymbol{\Sigma}_{IV,\lambda}=
 \frac{1}{N-1}\sum^{N}_{i=1}\left( \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}-\boldsymbol{\Sigma}_{IV,\lambda}\right) +\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i} \right)^{'} \\
&+\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\frac{1}{N-1}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}_{IV,i}-\boldsymbol{\theta}_{i}  \right) -\\
&\frac{N}{N-1}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}_{IVMG} \right)  =o_{p}(1).
\end{split}
\end{align}

Then, we can see that the asymptotic property of $\hat{\boldsymbol{\theta}}_{IVMG} $ as,
\begin{align}
\sqrt{N}\left(\hat{\boldsymbol{\theta}}_{IVMG}-\boldsymbol{\theta}  \right)\overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{IV,\lambda} \right).
\end{align}

\newpage

>>>>

\newpage
\tableofcontents
\newpage
\section{Model, asymptotic property of IV estimator}
\subsection{The models and Assumptions}
\subsubsection{Fixed effects model}
Consider the dynamic heterogeneous panels data model with fixed effects:
\begin{align}
\begin{split}
y_{i,t}&=\alpha_{i}+\phi_{i} y_{i,t-1}+ \boldsymbol{x}^{'}_{i,t}\boldsymbol{\beta}_{i}+u_{i,t}, \,\, for\,\,i=1,\ldots N;\,t=1,\ldots,T\, , \\
&= \boldsymbol{w}^{'}_{i,t}\boldsymbol{\theta}_{i}+ \alpha_{i}+u_{i,t}, \label{1}
\end{split}
\end{align}
where $\boldsymbol{x}_{i,t}$ and $\boldsymbol{\beta}_{i}$ are $k \times 1$ vectors, $\boldsymbol{\theta}_{i}=\left(\phi_{i}, \boldsymbol{\beta}^{'}_{i} \right)^{'}$ and $\boldsymbol{w}_{i,t}=\left(y_{i,t-1}, \boldsymbol{x}^{'}_{i,t} \right)^{'}$ is a $\left(1+k\right) \times 1$ vector.
Stacking the $T$ observations for each $i$, we have
\begin{align}
\boldsymbol{y}_{i}=\boldsymbol{W}_{i}\boldsymbol{\theta}_{i}+ \alpha_{i}\boldsymbol{\iota}_{T}+ \boldsymbol{u}_{i}, \label{2}
\end{align}
where $\boldsymbol{y}_{i}=\left(y_{i,1},\ldots, y_{i,T} \right)^{'}$, $\boldsymbol{W}_{i}=\left(\boldsymbol{w}_{i,1},\ldots, \boldsymbol{w}_{i,T} \right)^{'}$, $\iota_{T}=\left(1,\ldots,1 \right)^{'}$ and $\boldsymbol{u}_{i}=\left(u_{i,1}, \ldots, u_{i,T} \right)^{'}$.

@@

\subsection{IV estimation method and asymptotic property}
\citet{Norkute:2019} propose an IV estimator in dynamic heterogeneous panel data model. 
They use current and lagged values of $\boldsymbol{x}_{i}$ as instruments, as
\begin{align}
\boldsymbol{Z}_{i,t}=\left( \boldsymbol{x}_{i}, \boldsymbol{x}_{i,-1} \right)^{'},
\end{align}
where $\boldsymbol{Z}_{i}$ is $T \times  2k$ vector. \\

\begin{myAssu}
$\boldsymbol{A}_{i}=\plim_{T \to \infty}\tilde{\boldsymbol{A}}_{i,T}$ has full column rank, $\boldsymbol{B}_{i}=\plim_{T \to \infty}\tilde{\boldsymbol{B}}_{i,T}$ and $\boldsymbol{\Sigma}_{i}=\plim_{T \to \infty} T^{-1}\boldsymbol{Z}^{'}_{i}\boldsymbol{u}_{i} \boldsymbol{u}_{i}^{'}\boldsymbol{Z}$ has positive definite, uniformly, where $\tilde{\boldsymbol{A}}_{i,T}= \frac{1}{T}\boldsymbol{Z}^{'}_{i}\tilde{\boldsymbol{W}}^{b}_{i}$ and $\tilde{\boldsymbol{B}}_{i,T}= \frac{1}{T}\tilde{\boldsymbol{Z}}^{'}_{i}\boldsymbol{Z}_{i}$, \\
where $b = 1$ corresponds to the fixed effects model while $b = 2$ corresponds to the trend models.
\end{myAssu}

Then, the IV estimator can be expressed as
\begin{align}
\boldsymbol{\hat{\theta}}^{b}_{IV,i}=\left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{g}}_{i,T},
\end{align}
where
\begin{align}
\tilde{\boldsymbol{g}}_{i,T}=\frac{1}{T}\boldsymbol{Z}^{'}_{i}\tilde{\boldsymbol{y}}^{b}_{i},
\end{align}
 and $\tilde{\boldsymbol{W}}^{b}_{i}=\left( \tilde{w}^{b}_{i,1},\ldots, \tilde{w}^{b}_{i,T} \right)^{'}$ is $T \times 2k$ matrix

From above equation, we have
\begin{align}
\sqrt{T}\left(\boldsymbol{\hat{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i} \right)=\left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\left(T^{-1/2}  \boldsymbol{Z}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \right)
\end{align}
Then, the property of $T^{-1/2}  \boldsymbol{Z}^{'}_{i}\tilde{\boldsymbol{u}}_{i} $ is given by following proposition.\\
\begin{myProp}
Under above assumptions, as $\left(N, T \right)\overset{j}{\to} \infty$ such that $N/T \to c$ with $0 < c<\infty $, for each $i$, we have
\begin{align}
\begin{split}
&N^{-1} \boldsymbol{Z}^{'}_{i}\tilde{\boldsymbol{u}}_{i}\overset{p}{\to} \boldsymbol{0},  \\
&\,\,\,\,and\,\,\,\,\, \\
&T^{-1/2}  \boldsymbol{Z}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{i} \right).
\end{split}
\end{align}
\end{myProp}

Thus, IV  estimator, $\boldsymbol{\theta}^{b}_{IV, i}$ is $\sqrt{T}$ consistent to $\boldsymbol{\theta}_{i}$ and this estimator does not have Nickell's bias. Then, we have following theorem\\
$\mathbf{Theorem \,\,1}$ \\
As $\left(N,T \right)\to \infty $ such that $N/T \to c$ with $0< c< \infty$. for each $i$,
\begin{align}
\sqrt{T}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i}  \right)\overset{d}{\to} N \left(\boldsymbol{0},\,\left(\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}\boldsymbol{A}_{i} \right)^{-1}\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}   \boldsymbol{\Sigma}_{i}\boldsymbol{B}_{i}^{-1} \boldsymbol{A}_{i}\left(\boldsymbol{A}_{i}^{'}\boldsymbol{B}_{i}^{-1}\boldsymbol{A}_{i} \right)\right).
\end{align}

\subsubsection{Mean group IV estimator }
Now, we define the mean group estimator of $\boldsymbol{\theta}$:
\begin{align}
\hat{\boldsymbol{\theta}}^{b}_{IVMG}=\frac{1}{N}\sum^{N}_{i=1}\hat{\boldsymbol{\theta}}^{b}_{IVi}.
\end{align}
And we can show that the asymptotic property of $\hat{\boldsymbol{\theta}}_{IVMG}$, as
\begin{align}
\hat{\boldsymbol{\theta}}^{b}_{IVMG}-\boldsymbol{\theta}=\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}- \boldsymbol{\theta}\right)=\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}- \boldsymbol{\theta}_{i}\right)+\frac{1}{N}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i},
\end{align}
where
\begin{align}
\begin{split}
\frac{1}{N}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}- \boldsymbol{\theta}_{i}\right)&=\frac{1}{N}\sum^{N}_{i=1} \left(\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\tilde{\boldsymbol{A}}_{i,T} \right)^{-1}\tilde{\boldsymbol{A}}_{i,T}^{'}\tilde{\boldsymbol{B}}_{i,T}^{-1}\left(T^{-1}  \tilde{\boldsymbol{Z}}^{'}_{i}\tilde{\boldsymbol{u}}_{i} \right) \\
&= O_{p}\left(\delta^{-2}_{NT} \right),
\end{split}
\end{align}
where $\delta_{NT}=\min \{\sqrt{N},\,\sqrt{T} \}$.
We note that $\frac{1}{\sqrt{N}}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i}=O_{p}\left(N^{-1/2} \right)$, if $\delta_{NT}^{-(2+\varsigma)}\to 0$ for any $\varsigma >0$, we have
\begin{align}
\sqrt{N}\left(\hat{\boldsymbol{\theta}}^{b}_{IVMG}-\boldsymbol{\theta}  \right)=\frac{1}{\sqrt{N}}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i}+o_{p} \left(1 \right).
\end{align}

And the variance estimator of $\hat{\boldsymbol{\theta}}_{IVMG}$ is given by
\begin{align}
\hat{\boldsymbol{\Sigma}}_{IV,\lambda}=\frac{1}{N-1}\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}^{b}_{IV,i}- \hat{\boldsymbol{\theta}}^{b}_{IVMG}\right)\left( \hat{\boldsymbol{\theta}}^{b}_{IV,i}- \hat{\boldsymbol{\theta}}^{b}_{IVMG}\right)^{'}. \label{44}
\end{align}
Follow \citet{Norkute:2019}, we can show that $\hat{\boldsymbol{\Sigma}}_{IV,\lambda}$ is consistent and it does not have small $T$ bias.
Firstly, we decompose $(\ref{44})$ as
\begin{align}
\begin{split}
&\sum^{N}_{i=1}\left( \hat{\boldsymbol{\theta}}^{b}_{IV,i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}^{b}_{IVMG}\right)\left( \hat{\boldsymbol{\theta}}^{b}_{IV,i}- \boldsymbol{\theta}+\boldsymbol{\theta}-    \hat{\boldsymbol{\theta}}^{b}_{IVMG}\right)^{'}= \\
& \sum^{N}_{i=1} \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i} \right)^{'}+\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i}  \right) -\\
&N\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}^{b}_{IVMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}^{b}_{IVMG} \right). \label{45}
\end{split}
\end{align}
Then we can show consistent of $\hat{\boldsymbol{\Sigma}}^{b}_{IV,\lambda}$ as
\begin{align}
\begin{split}
&\hat{\boldsymbol{\Sigma}}^{b}_{IV,\lambda}-\boldsymbol{\Sigma}_{IV,\lambda}=
 \frac{1}{N-1}\sum^{N}_{i=1}\left( \boldsymbol{\lambda}_{i}\boldsymbol{\lambda}^{'}_{i}-\boldsymbol{\Sigma}_{IV,\lambda}\right) +\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i} \right)\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i} \right)^{'} \\
&+\frac{1}{N-1}\sum^{N}_{i=1}\left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i}  \right) \boldsymbol{\lambda}_{i}+\frac{1}{N-1}\sum^{N}_{i=1}\boldsymbol{\lambda}_{i} \left(\hat{\boldsymbol{\theta}}^{b}_{IV,i}-\boldsymbol{\theta}_{i}  \right) -\\
&\frac{N}{N-1}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}^{b}_{IVMG} \right)^{'}\left(\boldsymbol{\theta}-\hat{\boldsymbol{\theta}}^{b}_{IVMG} \right)  =o_{p}(1).
\end{split}
\end{align}

Then, we can see that the asymptotic property of $\hat{\boldsymbol{\theta}}_{IVMG} $ as,
\begin{align}
\sqrt{N}\left(\hat{\boldsymbol{\theta}}^{b}_{IVMG}-\boldsymbol{\theta}  \right)\overset{d}{\to} N\left(\boldsymbol{0},\boldsymbol{\Sigma}_{IV,\lambda} \right).
\end{align}

\section{Construction optimal instruments}
How to select optimal instruments is important issue in empirical studies.
\citet{Stephen:2001}, \citet{Kuersteiner:2010}, \citet{Ryo:2011}, \citet{Kang:2019} and \citet{Seojeong:2019} propose different methods to construct optimal instruments.
Here, we try to apply model average approach by \citet{Kuersteiner:2010} in here.

If we can observed long past periods variables, we have many instruments. In this case we define our instruments, as
\begin{align}
\boldsymbol{Z}^{(j)}_{i}=\left( \boldsymbol{x}_{i,\cdot}, \boldsymbol{x}_{i,-1},\ldots, \boldsymbol{x}_{i,-j} \right)^{'},
\end{align}
where $\boldsymbol{Z}^{(j)}_{i}$ is $T \times  (j+1)k$ matrix with $j \geq 1$. \\

@@

\citet{Kuersteiner:2010} provided model averaging two stage least squares estimator to balance the bias and efficiency. We try to follow this method to construct the optimal instruments. We define a weighting vector $\boldsymbol{H}=\left(h_{1}, \ldots, h_{j} \right)^{'}$. Then, we can weight $\boldsymbol{P}^{(j)}_{i}$ as
\begin{align}
\boldsymbol{P}\left(\boldsymbol{H} \right)= \sum^{J}_{j=1}h_{j} \boldsymbol{P}^{(j)}_{i},
\end{align}
where $J$ is maximum number of lagged variables that we can observed. 
Our goal is estimating $\boldsymbol{H}$ to minimize the approximate mean square error.

\newpage
\appendix
\appendixpage
\section{Asymptotic property of LS estimator}

@@
